### 2022-01-16 newvariant.tex
Thinking about kappa

In general, longer generation intervals lead to slower relative speed of the variant when the incidence of both strains is increasing (\fref{relspeed}, bottom panels) because slower growth of the variant reduces the differences in absolute speed.
When $\Rv=1$, the relative speed is insensitive to the generation-interval distribution of the variant because we always have $\rv=0$.
When $\Rv<1$, longer generation intervals of the variant lead to slower decay ($\rv$ closer to 0), and therefore, greater relative speed.
Once again, we see that assuming a narrower distribution (lower $\kappa$) has qualitatively similar effects as assuming a longer mean.

\fref{relspeed} also shows that when $\rho$ is fixed, relative speed depends on underlying epidemiological conditions---specifically, the absolute strength of the two strains. 
For example, even when the generation-interval distributions are identical ($\Gv=\Gw$, in this case), changing $\Rw$ from 0.49 to 1.27 (and thus $\Rv$ from 0.79 to 2.04) yields a relative speed $\delta$ between 0.08--0.11 for $\kappa=0.2$ and 0.06--0.14 for $\kappa=0.5$.
Differences in the generation-interval distributions exaggerate these changes.
Therefore, characterizing changes in the proportion of variants by assuming a fixed relative speed (e.g., by fitting a standard logistic growth curve \citep{switzerland2021variant} and using the resulting value of $\delta$) should be done with care.

>>>>

In general, longer generation intervals lead to slower relative speed of the variant when the incidence of both strains is increasing (\fref{relspeed}, bottom panels) because slower growth of the variant reduces the differences in absolute speed.
When $\Rv=1$, the relative speed is insensitive to the generation-interval distribution of the variant because we always have $\rv=0$.
When $\Rv<1$, longer generation intervals of the variant lead to slower decay ($\rv$ closer to 0), and therefore, greater relative speed.
Once again, we see that assuming a narrower distribution (lower $\kappa$) has qualitatively similar effects as assuming a longer mean.
\jd{This is very deep, and I don't think there's any ``once again'' here -- meaning, we haven't explained this one yet. This is the effect of lower $\kappa$ for both being compared to the effect of longer GI for just one. In the non-comparative version, the effect of high $\kappa$ is on the influential end: it's like longer (shorter) GIs when disease is decreasing (increasing).}

\fref{relspeed} also shows that when $\rho$ is fixed, relative speed depends on underlying epidemiological conditions---specifically, the absolute strength of the two strains. 
For example, even when the generation-interval distributions are identical ($\Gv=\Gw$, in this case), changing $\Rw$ from 0.49 to 1.27 (and thus $\Rv$ from 0.79 to 2.04) changes the relative speed $\delta$ from 0.08 to 0.11 when $\kappa=0.2$---and from 0.06 to 0.14 when $\kappa=0.5$.
Differences in the generation-interval distributions exaggerate these changes.
Therefore, characterizing changes in the proportion of variants by assuming a fixed relative speed (e.g., by fitting a standard logistic growth curve \citep{switzerland2021variant} and using the resulting value of $\delta$) should be done with care.
